VOI-aware MCTS

### 2012-06-10 paper/vago.ecai/case-for-support.tex
fixes

I, David Tolpin, am a full-time PhD student at the Department of
Computer Science at Ben-Gurion University of the Negev, Israel. For the last
three years, I have been researching {\it metareasoning in
  problem-solving search}, a field of Artificial Intelligence seeking
systematic approaches to development of heuristic algorithms for hard
problems. My and my advisor's joint paper, {\bf VOI-aware MCTS},
presenting a result of the ongoing result, has been accepted to
ECAI~2012 for poster presentation.

@@

\begin{itemize}
\item registration --- \euro{120}
\item accomodation --- \euro{180} (student room)
\item airplane tickets --- \euro{680} (current lowest available rate
  from the current travel agent)
\end{itemize}

>>>>

I, David Tolpin, am a full-time PhD student at the Department of
Computer Science at Ben-Gurion University of the Negev, Israel. For the last
three years, I have been researching {\it metareasoning in
  problem-solving search}, a field of Artificial Intelligence seeking
systematic approaches to development of heuristic algorithms for hard
problems. My and my advisor's joint paper, {\bf VOI-aware MCTS},
presenting a result of ongoing research, has been accepted to
ECAI~2012 for poster presentation.

@@

\begin{itemize}
\item registration --- \euro{120}
\item accomodation --- \euro{180} (student room)
\item airplane tickets --- \euro{680} (current lowest available rate
  from the local travel agent)
\end{itemize}
